Databrary: Enabling sharing and reuse of research video

### 2015-04-23 jcdl-15/demo.tex
few changes for submission

\begin{abstract}
Video and audio recordings serve as a primary data source in many fields, especially in the social and behavioral sciences.
Recordings present unique opportunities for reuse and reanalysis for novel scientific purposes, but also present challenges due around respecting the privacy of individuals depicted.
Databrary is a web-based service for sharing and reusing the video data created by researchers in the developmental and learning sciences.
By investigating how researchers organize, analyze, and mine their own recordings, we have implemented a system that empowers researchers to capture, store, and share recordings in a standardized way.
This demo will provide a tour through the Databrary service, highlighting how it promotes storage, management, sharing, and reuse of research data, controls access privileges to restricted human subject data, and facilitates browsing and discoverability of datasets.
\end{abstract}

@@

Databrary began accepting contributions in early 2014 and opened for general use in October 2014.
As of April 2015, it hosts 7,300 video files totaling 2,400 hours of recordings along with 2,600 additional files.
These files make up 3,100 study sessions and are covered by 2,000 metadata records (including 1,800 individual participants).
Data originate from 35 individual contributors across 25 different universities. 50 universities have granted access to the repository to over 95 researchers.

@@

Focusing on a particular research domain allows us to develop tools informed by how the intended community of users currently works, while accommodating the specific privacy concerns for data that often have a high disclosure risk.
We have created a set of data management features that empower researchers to actively manage their own projects---to upload data with accompanying metadata---as each study unfolds. 
These features include a spreadsheet interface for entering, editing, and viewing the metadata for all sessions related to a study.
Session-level metadata might include participant details, conditions of study, tasks in the experiment, permission levels, study groups, or conditions, and serves the purpose of providing ways to browse and search for specific video data in Databrary. 
We have found that most researchers use desktop spreadsheets for managing data in their own labs, making the interface and functionality intuitive to users.

@@

As we continue to gather feedback from our user base, we not only see Databrary as a tool that facilitates the standardized management of research data, but also as an opportunity to enhance the ability for academics to communicate about and enhance their own research.
We have already addressed the basic upload, data management, and storage needs of our target community, and have sufficiently answered the question of how to protect sensitive video data while providing wider opportunities to share those data.
Going forward, we hope to focus more on developing the tools for searching, discovering, and reusing those data, allowing researchers to work with their data in ways they had not previously imagined.

>>>>

\begin{abstract}
Video and audio recordings serve as a primary data source in many fields, especially in the social and behavioral sciences.
Recordings present unique opportunities for reuse and reanalysis for novel scientific purposes, but also present challenges related to respecting the privacy of individuals depicted.
Databrary is a web-based service for sharing and reusing the video data created by researchers in the developmental and learning sciences.
By investigating how researchers organize, analyze, and mine their own recordings, we have implemented a system that empowers researchers to capture, store, and share recordings in a standardized way.
This demo will provide a tour through the Databrary service, highlighting how it promotes storage, management, sharing, and reuse of research data, controls access privileges to restricted human subject data, and facilitates browsing and discoverability of datasets.
\end{abstract}

@@

Databrary began accepting contributions in early 2014 and opened for general use in October 2014.
As of April 2015, it hosts 7,300 video files totaling 2,400 hours of recordings along with 2,600 additional files.
These files make up 3,100 study sessions and are covered by 2,000 metadata records (including 1,800 individual participants).
Data originate from 35 individual contributors across 25 different universities. Fifty universities have granted access to the repository to over 95 researchers.

@@

Focusing on a particular research domain allows us to develop tools informed by how the intended community of users currently works, while accommodating the specific privacy concerns for data that often have a high disclosure risk.
We have created a set of data management features that empower researchers to actively manage their own projects---to upload data with accompanying metadata---as each study unfolds. 
These features include a spreadsheet interface for entering, editing, and viewing the metadata for all sessions related to a study.
Session-level metadata might include participant details, tasks in the experiment, permission levels, study groups, or conditions, and serves the purpose of providing ways to browse and search for specific video data in Databrary. 
We have found that most researchers use desktop spreadsheets for managing data in their own labs, making the interface and functionality intuitive to users.

@@

As we continue to gather feedback from our user base, we not only see Databrary as a tool that facilitates the standardized management of research data, but also as an opportunity to enhance the ability for academics to communicate about and bolster their own research.
We have already addressed the basic upload, data management, and storage needs of our target community, and have sufficiently answered the question of how to protect sensitive video data while providing wider opportunities to share those data.
Going forward, we hope to focus more on developing the tools for searching, discovering, and reusing those data, allowing researchers to work with their data in ways they had not previously imagined.
